### 2018-04-28 paper/building-blocks.tex

\((\vk, C, \sigma)\gets \DeBEenc[\mpk, m, S]\):
takes a message \(m\) and a recipient set \(S\), it then encrypts the message 
for each recipient's key, signs the tuple of all ciphertexts and returns the 
verification key, ciphertexts and signature.
(Note that the signature does not authenticate the sender, it ties the 
ciphertext together and is needed for correctness, we refer to~\cite{ANOBE} for 
details.)

@@

      \Function{$\DeBEenc$}{$\mpk, m, S$}
        \State $(\ssk, \vk)\gets \Sign[Keygen]$
        \State Choose a random permutation \(\pi\colon S\to S\).
        \For{$i \in S$}
          \State $c_i\gets \Enc[Enc](\pk_i, m\concat \vk)$
        \EndFor
        \State $C\gets ( c_{\pi(1)}, \dotsc, c_{\pi(|S|)} )$
        \State $\sigma\gets \Sign[Sign](\ssk, C)$
        \State \Return $(\vk, C, \sigma)$
      \EndFunction

>>>>

\((\vk, C, \sigma)\gets \DeBEenc[\mpk, S, m]\):
takes a message \(m\) and a recipient set \(S\), it then encrypts the message 
for each recipient's key, signs the tuple of all ciphertexts and returns the 
verification key, ciphertexts and signature.
(Note that the signature does not authenticate the sender, it ties the 
ciphertext together and is needed for correctness, we refer to~\cite{ANOBE} for 
details.)

@@

      \Function{$\DeBEenc$}{$\mpk, S, m$}
        \State $(\ssk, \vk)\gets \Sign[Keygen]$
        \State Choose a random permutation \(\pi\colon S\to S\).
        \For{$i \in S$}
          \State $c_i\gets \Enc[Enc](\pk_i, m\concat \vk)$
        \EndFor
        \State $C\gets ( c_{\pi(1)}, \dotsc, c_{\pi(|S|)} )$
        \State $\sigma\gets \Sign[Sign](\ssk, C)$
        \State \Return $(\vk, C, \sigma)$
      \EndFunction
